Turbulence in compact to giant HII regions

### 2022-05-27 strucfunc_paper.tex
Compare with precious studies of Lagoon strucfunc

>>>>

The structure function of the Lagoon Nebula was previously
studied by \citet{Chakraborty:1999a} using the [\ion{O}{3}] \Wav{5007} line,
finding an approximate power law behavior (\(m = 0.46\))
on scales of \num{0.01} to \SI{0.2}{pc}.
No flattening of the structure function at the largest scales
was seen,
but that is to be expected due to the finite box effect
(see Appendix~\ref{sec:finite-box-effects})
given that we determine the correlation length to be \(r_0 \approx   \SI{1}{pc}\) for this nebula,
which is several times larger than the region mapped by \citet{Chakraborty:1999a}.
On the other hand, the magnitude of the velocity dispersion found by these authors much larger than we measure.
For instance, they find \(B(r) = \SI{278}{km^2.s^{-1}}\) at \SI{0.2}{pc}, whereas we find \(B(r) \approx \SI{2}{km^2.s^{-1}}\) at the same scale, which corresponds to a discrepancy of more than a factor of a hundred in \(\sigma^2\pos\).
This may be due in part to the fact that \citet{Chakraborty:1999a}
observed a small and atypical part of the nebula known as the
Hourglass region, which includes a cluster of very young stars
\citep{Arias:2006e}.
